---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Genomics boilerplate in Plotly

> _"Reproducible research is important!"_
>
> `r tufte::quote_footer('Every grad student at some point')`

I realized copy/pasting **a lot** of code when it comes to visualization, 
so why not keeping them somewhere I can easily reach out and plug in whenever I need them, right?   
Right.




Let's use a dataset from my package (because why not?)
```{r}
library(cinaR) # my package
library(dplyr) # important
library(purrr) # important
library(plotly)# stuff
```

```{r my package rocks, cache=TRUE}
# data, lol
bed <- cinaR::bed

# we need this
contrasts<- c("B6", "B6", "B6", "B6", "B6", "NZO", "NZO", "NZO", "NZO", "NZO", "NZO",
              "B6", "B6", "B6", "B6", "B6", "NZO", "NZO", "NZO", "NZO", "NZO", "NZO")

# let's use my package to find some results (why NOT?)
# if you want to learn more about it just check the package, it is all free!
results <- cinaR(bed, contrasts, reference.genome = "mm10", DA.fdr.threshold = 1, verbose = F)
```


okay, let's get the results and put them into separate variables.
```{r}
# peaks by sample
all.peaks <- results$DA.results$cp

# differential peaks (and their info)
da.peaks <- results$DA.results$DA.peaks$B6_NZO

# enrichment of pathways (and their info)
enrichments <- results$Enrichment.Results$B6_NZO

# color values I like
colors <- cinaR::color_values
```

## Good stuff

Just check this mice data with your mouse (what a bad joke!)

### Volcano plot
```{r}
volcano.fig <- plot_ly(da.peaks, 
        x = ~logFC, y = ~-log(FDR), type = 'scatter',
        hoverinfo = "text", color = ~ifelse(FDR < 0.01, "DA", "Non-DA"), colors = c("red", "darkblue"),
        text = ~paste('</br> Gene Name: ', ifelse(is.na(gene_name), transcriptId, gene_name),
                      '</br> FDR: ', sprintf("%0.2g", FDR),
                      '</br> log(FC): ', sprintf("%2.2f", logFC)
                    )
      )

volcano.fig <- volcano.fig %>% 
    config(displayModeBar = FALSE) %>%  # no band 
    layout(xaxis = list(range = c(-6, 6))) %>% # make it centered
    toWebGL() # print to canvas to make it faster

volcano.fig
```

### Box plot
```{r}
# select Kif11 peak: chr19_37374896_37377150
kif11.peak <- all.peaks["chr19_37374896_37377150",]

# create cute df
df.plot <- data.frame(exp = as.numeric(kif11.peak), contrasts = contrasts, row.names = NULL, stringsAsFactors = FALSE)

boxplot.fig <- plot_ly(df.plot, 
        x = ~contrasts, y = ~exp, 
        type = 'box', color = ~contrasts
      )

boxplot.fig <- boxplot.fig %>% 
    config(displayModeBar = FALSE) %>%  # no band 
    layout(title = "Kif11 accesibility levels",
           xaxis = list(title = "Strain"),
           yaxis = list(title = "log(cpm)")) %>% 
    toWebGL()  # print to canvas to make it faster

boxplot.fig
```

### Dot plot
```{r}
dot.fig <- plot_ly(enrichments, 
                   x = "B6 vs NZO", y = ~module.name, size = ~ifelse(adj.p == 1, NA, -log(adj.p)), 
                   type = 'scatter', color = ~ status, colors = color_values,
                   hoverinfo = 'text',
                   text = ~paste(
                       '</br> Pathway: ', module.name,
                       '</br> FDR: ', sprintf('%1.2g', adj.p),
                       '</br> Status: ', status,
                       '</br> Overlapping genes: ', overlapping.genes
                   )
)

dot.fig
```

### Heatmap
For heatmaps there is a package called `heatmaply` which is a wrapper over `plotly` itself
```{r}
library(heatmaply)

# select myeloid genes
selected.genes <- vp2008$`Myeloid lineage 2`

# find their chr_start_end
selected.genes.loc <- da.peaks[toupper(da.peaks$gene_name) %in% selected.genes, c("Row.names", "gene_name")]

locs <- selected.genes.loc$Row.names

# ready!
pheatmap.data <- all.peaks[locs,]

rownames(pheatmap.data) <- selected.genes.loc$gene_name

# go
heatmaply(pheatmap.data, scale = "row", 
          scale_fill_gradient_fun = 
            ggplot2::scale_fill_gradient2(
              low = color_values["Closing"], 
              high = color_values["Opening"], 
              midpoint = 0
            )
)
```

> _"This might not be very reproducible!"_
>
> `r tufte::quote_footer('Every grad student at some point')`


